A Multi-telescope Campaign on \frb: Implications for the FRB Population

### 2017-05-21 repeater-vladata.tex
changed gaussian norm in equation
final run of notebooks

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for the three VLA bursts with observing coverage by Arecibo or Effelsberg. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $64\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.8$ and $\alpha_{3/4.5}<-2.7$. These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.

@@

The dynamic radio spectra (time versus frequency) were modeled using a Markov chain Monte Carlo (MCMC) method. We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled prior to dispersion correction. The spectral structure was modeled as a broad Gaussian envelope as:
\begin{equation}
G(\nu) = \frac{\rm{A}}{\sqrt{2\pi} \sigma} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
\end{equation}
\noindent where ``A'' is in mJy per 5~ms integration, $\nu_0$\ is the Gaussian center frequency, and $\sigma$\ is its width. The arrival time was modeled with a cold plasma dispersion law with the arrival time in units of integrations of:
\begin{equation}
\rm{i} (\nu) = \rm{i0} + 4.1488\times10^{-3}\ \rm{DM} \left(\nu^{-2} - \nu_0^{-2}\right)/(5 \rm{ms})
\end{equation}
\noindent where ``i0'' is the arrival integration at the highest frequency and $\nu$\ is in units of GHz. Finally, the pulses were assumed to have an intrinsically square temporal width (parameter $W_{int}$). These 6 parameters defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.

>>>>

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for the three VLA bursts with observing coverage by Arecibo or Effelsberg. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $57\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.1$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.5}<-2.7$. These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.

@@

The dynamic radio spectra (time versus frequency) were modeled using a Markov chain Monte Carlo (MCMC) method. We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}. The dynamic spectra were modeled prior to dispersion correction. The spectral structure was modeled as a broad Gaussian envelope as:
\begin{equation}
G(\nu) = \rm{A} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
\end{equation}
\noindent where ``A'' is in mJy per 5~ms integration, $\nu_0$\ is the Gaussian center frequency, and $\sigma$\ is its width. The arrival time was modeled with a cold plasma dispersion law with the arrival time in units of integrations of:
\begin{equation}
\rm{i} (\nu) = \rm{i0} + 4.1488\times10^{-3}\ \rm{DM} \left(\nu^{-2} - \nu_0^{-2}\right)/(5 \rm{ms})
\end{equation}
\noindent where ``i0'' is the arrival integration at the highest frequency and $\nu$\ is in units of GHz. Finally, the pulses were assumed to have an intrinsically square temporal width (parameter $W_{int}$). These 6 parameters defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.
